### 2017-11-26 paper/sections/2_parsplice-keyspace-analysis.tex
paper: spellcheck
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

\subsubsection*{Experimental Setup} All experiments ran on Trinitite, a Cray
XC40 with 32 Intel Haswell 2.3GHz cores per node.  Each node has 128GB of RAM
and our goal is to limit the size of the cache to 3\% of RAM . Note that this
is an addition to the 30GB that ParSplice uses to manage other ranks on the
same node.  A single Cray node produced trajectories that are \(5\times\) times
longer than our 10 node CloudLab clusters and \(25\times\) longer than our 10
node cluster at UCSC. As a result, it reaches different job phases faster and
gives us a more comprehensive view of the workload. The performance gains
compared to the commodity clusters have more to do with memory/PCI bandwidth
than network.

>>>>

\subsubsection*{Experimental Setup} All experiments ran on Trinitite, a Cray
XC40 with 32 Intel Haswell 2.3GHz cores per node.  Each node has 128GB of RAM
and our goal is to limit the size of the cache to 3\% of RAM . Note that this
is an addition to the 30GB that ParSplice uses to manage other ranks on the
same node.  A single Cray node produced trajectories that are \(5\times\) times
longer than our 10 node CloudLab clusters and \(25\times\) longer than our 10
node cluster at UC Santa Cruz. As a result, it reaches different job phases faster and
gives us a more comprehensive view of the workload. The performance gains
compared to the commodity clusters have more to do with memory/PCI bandwidth
than network.

### 2017-11-26 paper/sections/4_dynamic-policies.tex
paper: spellcheck
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

Figure~\ref{src:dyn-cache} shows the algorithm we use to detect groups of key
access patterns, which we call ``fans". Iterating backwards through the key
access trace, at each time ste`p we find the lowest key ID and compare against
the lowest key ID we have seen so far (Line 7). We also maintain the top and
bottom of each group of key accesses (Line 13) so we can tell the ``how much"
policy the number of keys to evict (Line 19).  The algorithm iterates backwards
over the key access trace because a change in the minimum value signals a new
group of key accesses. No signal exists iterating left to right, as the maximum
value always increases and the minimum values at the bottom of each group of
key accesses are sparse.  For example, the maximum distance between values
along the bottom edge of the zoomed group of key accesses in
Figure~\ref{fig:keyspace-zoomed} is 125 seconds, while the maximum distance
between minimum values for the group of key accesses before is 0 seconds. As a
result of this sparseness, iterating left to right requires a ``window size"
parameter to determine when we think a minimum value will not show up again.
We exchange runtime, in the form of an O(\(n\)) algorithm where \(n\) is the
number events, for simplicity because this approach avoids adding new
thresholds for key access pattern detection ({\it e.g.}, space between key
accesses, space between key IDs, and window size of consecutive key accesses).

@@

if #fans < 2 then return false else
  WRstate(fans[#fans-1]['top']-fans[1]['bottom'])
  return true
end
\end{minted}
\caption{The dynamically sized cache policy, whose performance is shown in 
Figure~\ref{fig:cache-management}, iterates backwards over timestamp-keyID pairs
and detects when key accesses move on to a new subset of
keys. We refer to groups of key accesses as ``fans".\label{src:dyn-cache}}
\end{figure}

>>>>

Figure~\ref{src:dyn-cache} shows the algorithm we use to detect groups of key
access patterns, which we call ``fans". Iterating backwards through the key
access trace, at each time step we find the lowest key ID and compare against
the lowest key ID we have seen so far (Line 7). We also maintain the top and
bottom of each group of key accesses (Line 13) so we can tell the ``how much"
policy the number of keys to evict (Line 19).  The algorithm iterates backwards
over the key access trace because a change in the minimum value signals a new
group of key accesses. No signal exists iterating left to right, as the maximum
value always increases and the minimum values at the bottom of each group of
key accesses are sparse.  For example, the maximum distance between values
along the bottom edge of the zoomed group of key accesses in
Figure~\ref{fig:keyspace-zoomed} is 125 seconds, while the maximum distance
between minimum values for the group of key accesses before is 0 seconds. As a
result of this sparseness, iterating left to right requires a ``window size"
parameter to determine when we think a minimum value will not show up again.
We exchange runtime, in the form of an O(\(n\)) algorithm where \(n\) is the
number events, for simplicity because this approach avoids adding new
thresholds for key access pattern detection ({\it e.g.}, space between key
accesses, space between key IDs, and window size of consecutive key accesses).

@@

if #fans < 2 then return false else
  WRstate(fans[#fans-1]['top']-fans[1]['bottom'])
  return true
end
\end{minted}
\caption{The dynamically sized cache policy, whose performance is shown in 
Figure~\ref{fig:cache-management}, iterates backwards over timestamp-key pairs
and detects when key accesses move on to a new subset of
keys. We refer to groups of key accesses as ``fans".\label{src:dyn-cache}}
\end{figure}
